---
title: "gapsa-flash-reports"
author: "Emily Hu"
date: '2022-07-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(qualtRics)
library(tidyverse)
```

```{r}
## todo -- copy in qualtrics credentials!!

surveys <- all_surveys()
flashreport_survey_id <- (surveys %>% filter(name == "GAPSA Flash Report Form (2022-23) V2"))$id
```

```{r}
df.gaspa_response <- fetch_survey(
  surveyID = flashreport_survey_id,
  save_dir = ".",
  force_request = TRUE
)

df.gaspa_response %>% head()
```

Process the Submissions
#1_ ... [subitem_name]
#2_ ... [date]
#3_ ... [budget_code]
#4_ ... [vendor]
#5_ ... [description]
#6_ ... [payment_mode]
#7_ ... [payment_number]
#8_ ... [amount_spent]
#9_ ... [status]
#10_ ... [notes]

```{r}
budget_summary <- df.gaspa_response %>%
  select(email, month, year, grep("main", names(df.gaspa_response))) %>%
  mutate(across(everything(), as.character)) %>%
  pivot_longer(-c(email, month, year), names_to = "main") %>%
  mutate(
    main = sub("main", "", main),
    main = sub("#1_", "subitem_name ", main),
    main = sub("#2_", "date ", main),
    main = sub("#3_", "budget_code ", main),
    main = sub("#4_", "vendor ", main),
    main = sub("#5_", "description ", main),
    main = sub("#6_", "payment_mode ", main),
    main = sub("#7_", "payment_number ", main),
    main = sub("#8_", "amount_spent ", main),
    main = sub("#9_", "status ", main),
    main = sub("#10_", "notes ", main),
    main = sub(" .*", "", main)
  ) %>%
  group_by(email, month, year, main) %>%
  mutate(row = row_number()) %>%
  pivot_wider(names_from = "main") %>%
  select(-row) %>%
  drop_na(subitem_name)
```

```{r}
budget_summary %>% write_csv('budget_summary_new.csv')
```


# OLD CODE FOR PREVIOUS VERSION#

Check in on the Monthly Spending Goals (MSG)'s

msg_checkin
#1_ ... [name of subitem]
#2_ ... [allocated]
#3_ ... [used]

```{r}
# msgcheckin_cleaned <- df.gaspa_response %>%
#   select(email, month, year, grep("msg_checkin", names(df.gaspa_response))) %>%
#   mutate(across(everything(), as.character)) %>%
#   pivot_longer(-c(email, month, year), names_to = "msg_checkin") %>%
#   mutate(
#     msg_checkin = sub("msg_checkin", "", msg_checkin),
#     msg_checkin = sub("#1_", "subitem_name ", msg_checkin),
#     msg_checkin = sub("#2_", "amt_allocated ", msg_checkin),
#     msg_checkin = sub("#3_", "amt_used ", msg_checkin),
#     msg_checkin = sub(" .*", "", msg_checkin)
#   ) %>%
#   group_by(email, month, year, msg_checkin) %>%
#   mutate(row = row_number()) %>%
#   pivot_wider(names_from = "msg_checkin") %>%
#   select(-row) %>%
#   drop_na(subitem_name)
```

```{r}
# msgcheckin_cleaned %>% write_csv('msg_summary.csv')
```


paid
#1_ ... [name of subitem]
- number after _ is the nth row
#2_ ... [date]
#3_ ... [vendor]
#8_ ... [budget code]
#4_ ... [invoice]
#5_ ... [amount]
#6_ ... [description]
#7_ ... [notes]

```{r}
# paid_cleaned <- df.gaspa_response %>%
#   select(email, month, year, grep("paid", names(df.gaspa_response))) %>%
#   mutate(across(everything(), as.character)) %>%
#   pivot_longer(-c(email, month, year), names_to = "paid") %>%
#   mutate(
#     paid = sub("paid", "", paid),
#     paid = sub("#1_", "subitem_name ", paid),
#     paid = sub("#2_", "date ", paid),
#     paid = sub("#3_", "vendor ", paid),
#     paid = sub("#4_", "invoice ", paid),
#     paid = sub("#5_", "amount ", paid),
#     paid = sub("#6_", "description ", paid),
#     paid = sub("#7_", "notes ", paid),
#     paid = sub("#8_", "budget_code ", paid),
#     paid = sub(" .*", "", paid),
#     status = "paid"
#   ) %>%
#   group_by(email, month, year, paid) %>%
#   mutate(row = row_number()) %>%
#   pivot_wider(names_from = "paid") %>%
#   select(-row) %>%
#   drop_na(subitem_name) %>%
#   unique()
# 
# submitted_cleaned <- df.gaspa_response %>%
#   select(email, month, year, grep("submitted", 
#                   names(df.gaspa_response))) %>%
#   mutate(across(everything(), as.character)) %>%
#   pivot_longer(-c(email, month, year), names_to = "submitted") %>%
#   mutate(
#     submitted = sub("submitted", "", submitted),
#     submitted = sub("#1_", "subitem_name ", submitted),
#     submitted = sub("#2_", "date ", submitted),
#     submitted = sub("#3_", "vendor ", submitted),
#     submitted = sub("#4_", "invoice ", submitted),
#     submitted = sub("#5_", "amount ", submitted),
#     submitted = sub("#6_", "description ", submitted),
#     submitted = sub("#7_", "notes ", submitted),
#     submitted = sub("#8_", "budget_code ", submitted),
#     submitted = sub(" .*", "", submitted),
#     status = "submitted"
#   ) %>%
#   group_by(email, month, year, submitted) %>%
#   mutate(row = row_number()) %>%
#   pivot_wider(names_from = "submitted") %>%
#   select(-row) %>%
#   drop_na(subitem_name) %>%
#   unique()
# 
# expected_cleaned <- df.gaspa_response %>%
#   select(email, month, year, grep("expected", 
#                                   names(df.gaspa_response))) %>%
#   mutate(across(everything(), as.character)) %>%
#   pivot_longer(-c(email, month, year), names_to = "expected") %>%
#   mutate(
#     expected = sub("expected", "", expected),
#     expected = sub("#1_", "subitem_name ", expected),
#     expected = sub("#2_", "date ", expected),
#     expected = sub("#3_", "vendor ", expected),
#     expected = sub("#4_", "invoice ", expected),
#     expected = sub("#5_", "amount ", expected),
#     expected = sub("#6_", "description ", expected),
#     expected = sub("#7_", "notes ", expected),
#     expected = sub("#8_", "budget_code ", expected),
#     expected = sub(" .*", "", expected),
#     status = "expected"
#   ) %>%
#   group_by(email, month, year, expected) %>%
#   mutate(row = row_number()) %>%
#   pivot_wider(names_from = "expected") %>%
#   select(-row) %>%
#   drop_na(subitem_name) %>%
#   unique()
```

Export a summary of the budget

```{r}
# budget_items_all <- paid_cleaned %>% rbind(submitted_cleaned) %>%
#  rbind(expected_cleaned) %>% 
#   select(email, month, year, date, status,
#          subitem_name, amount, vendor,
#          budget_code, invoice,
#          description, notes)
# 
# budget_items_all %>% write_csv('budget_summary.csv')
```
